### 2008-08-01 doc/backend_interface/Backends.tex
Major restructuring

This document describes the Advanced Resource Connector~\cite{arc1}
batch system back-end infrastrucure. It aims to describe the infrastructure
in enough detail that a developer can add a new local resource management
system (LRMS) to the ARC middleware. It also intends to serve as a
reference manual describing existing batch system interfaces. Note
that the current solution described in this manual is not a real interface,
it is too diffuse to be that.

The batch system back-ends are what tie the ARC grid middleware (through
(ARC Resource-coupled EXecution servcie, A-REX~\cite{arex}) to the underlying
cluster management system or LRMS. The back-ends consist of set of shell and
Perl scripts whose role are twofold:

@@

\begin{quote}
Parses a config file. It returns exit status 1 if the file cannot
be read, or 0 otherwise. Badly formed lines are silently ignored.
Option values can be surrounded by sigle quotes or double quotes.
Values without quotes are also accepted. Multi-valued options are
not supported currently. Only the last defined value is retained. 
\end{quote}
\texttt{config\_update\_from\_section <section\_name>}

@@

The information collector scripts are divided between several seperate scripts:
\begin{itemize}
\item \texttt{cluster+qju.pl} - driver for information collection. It calls all other infomation collectors and prints results in XML. The information collection is done by one single invocation of this script
\item \texttt{InfoCollector.pm} - base class for all information collectors (i.e.: all files \texttt{*Info.pm})
\item \texttt{InfoChecker.pm} - used by InfoCollector to validate options and results against a simple 'schema' (not XML Schema)
\item \texttt{GMJobsInfo.pm} - collects information about jobs from grid manager status files
\item \texttt{HostInfo.pm} - collects other information that can be collected on the front end (hostname, software version, disk space for users, installed certificates, Runtime environments ...)
\item \texttt{LRMSInfo.pm} - collects information that is LRMS specific (queues, jobs, local user limits ...)
\item \texttt{BATCH\_SYSTEM\_NAME.pm} - plugins for LRMSInfo. Only Fork, SGE and PBS are updated to the new framework
\item \texttt{ARC0ClusterInfo.pm} - combines all information about A-REX and produces information structured according to the classic NG schema
\item \texttt{ARC1ClusterInfo.pm} - combines all information about A-REX and produces information structured according to the GLUE2 schema
\item \texttt{ARC0ClusterSchema.pm} - description of the info produced by ARC0ClusterInfo
\item \texttt{ARC1ClusterSchema.pm} - description of the info produced by ARC1ClusterInfo
\end{itemize}

All information about the hosting environment and queues is collected by one invocation of the perl script named
\texttt{cluster+qju.pl}. The XML output is printed to \texttt{STDOUT} and it includes
two representations of the output data, namely the classic NorduGrid information schema and an incomplete GLUE2 schema representation.

@@

Sun Grid Engine, formely known as Codine, is an open source batch
system maintained by Sun. Runs on Linux, Solaris.

@@

Set up one or more SGE queues for access by grid users. Queues can
be shared by normal and grid users. In case you want to set up nore
than one ARC queue, make sure that the corresponding SGE queues have
no shared nodes among them. Otherwise the counts of free and occupied
CPUs might be wrong. Only SGE versions 6 and above are supported.

>>>>

This document describes the Advanced Resource Connector~\cite{arc1}
batch system back-end infrastructure. It aims to describe the infrastructure
in enough detail that a developer can add a new local resource management
system (LRMS) to the ARC middleware. It also intends to serve as a
reference manual describing existing batch system interfaces. Note
that the current solution described in this manual is not a real interface,
it is too diffuse to be that.

The batch system back-ends are what tie the ARC grid middleware (through
(ARC Resource-coupled EXecution service, A-REX~\cite{arex}) to the underlying
cluster management system or LRMS. The back-ends consist of set of shell and
Perl scripts whose role are twofold:

@@

\begin{quote}
Parses a config file. It returns exit status 1 if the file cannot
be read, or 0 otherwise. Badly formed lines are silently ignored.
Option values can be surrounded by single quotes or double quotes.
Values without quotes are also accepted. Multi-valued options are
not supported currently. Only the last defined value is retained. 
\end{quote}
\texttt{config\_update\_from\_section <section\_name>}

@@

The information collector scripts are divided between several separate scripts:
\begin{itemize}
\item \texttt{cluster+qju.pl} - driver for information collection. It calls all other information collectors and prints results in XML. The information collection is done by one single invocation of this script
\item \texttt{InfoCollector.pm} - base class for all information collectors (i.e.: all files \texttt{*Info.pm})
\item \texttt{InfoChecker.pm} - used by InfoCollector to validate options and results against a simple 'schema' (not XML Schema)
\item \texttt{GMJobsInfo.pm} - collects information about jobs from grid manager status files
\item \texttt{HostInfo.pm} - collects other information that can be collected on the front end (hostname, software version, disk space for users, installed certificates, Runtime environments ...)
\item \texttt{LRMSInfo.pm} - collects information that is LRMS specific (queues, jobs, local user limits ...)
\item \texttt{BATCH\_SYSTEM\_NAME.pm} - plugins for LRMSInfo. Only Fork, SGE and PBS are updated to the new framework
\item \texttt{ARC0ClusterInfo.pm} - combines all information about A-REX and produces information structured according to the classic NG schema
\item \texttt{ARC1ClusterInfo.pm} - combines all information about A-REX and produces information structured according to the GLUE2 schema
\item \texttt{ARC0ClusterSchema.pm} - description of the info produced by ARC0ClusterInfo
\item \texttt{ARC1ClusterSchema.pm} - description of the info produced by ARC1ClusterInfo
\end{itemize}

All information about the hosting environment and queues is collected by one invocation of the Perl script named
\texttt{cluster+qju.pl}. The XML output is printed to \texttt{STDOUT} and it includes
two representations of the output data, namely the classic NorduGrid information schema and an incomplete GLUE2 schema representation.

@@

Sun Grid Engine, formerly known as Codine, is an open source batch
system maintained by Sun. Runs on Linux, Solaris.

@@

Set up one or more SGE queues for access by grid users. Queues can
be shared by normal and grid users. In case you want to set up more
than one ARC queue, make sure that the corresponding SGE queues have
no shared nodes among them. Otherwise the counts of free and occupied
CPUs might be wrong. Only SGE versions 6 and above are supported.
